Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-21 PaperBCJ.tex

Deep Learning has played an important role in modern times, being widely used in artificial vision applications and specifically in pattern recognition. The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture. This paper presents a study of a convolutional neural network with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages. The algorithm has two stages, segmentation of images and classification. Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two classes by means of a convolutional neural network previously trained with a dataset generated through the segmentation stage. The performance of the network was analyzed and compared with different network architectures. The network architecture that presented the best training results was chosen, we experimented by modifying its number of filters, to analyze their behavior. Finally, the resulting network was tested on different processors to compare classification times.\\

\begin{comment}
-Deep Learning ha tenido un papel muy importante en los tiempos modernos, siendo muy utilizado en vision artificial y especialmente en reconocimiento de patrones, lo cual abre muchas puertas en los campos de aplicacion siendo uno de ellos la agricultura de presicion.En este paper presentamos el estudio una red neuronal convolucional aplicada a la clasificacion de plantas de maiz y de mala hierba en tiempo real, dirigida a campos de maiz en su etapa inicial.El algoritmo cuenta con dos etapas, segmentacion de imagenes y la clasificacion. En la segmentacion se busca separar de la imagen las plantas de forma individual. Mientras que la clasificacion se da a traves de la red neuronal convolucional, previamente entrenada con un dataset generado mediante la etapa de segmentacion. El rendimiento de la red se ilustra mediante analisis y comparaciones con diferentes arquitecturas de red, luego con la red que presento mejores resultados, se experimeto modificando su numero de filtros, para analizar su comportamiento. Finalmente con la red resultante se implemet\'o en diferentes procesadores para comparar tiempos de clasificacion.
\end {comment}
\end{abstract}

@@

Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with industrial revolution. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources make it impossible for the country to exploit its true potential as an agricultural producer. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality. 
\\

Nowadays, one of agriculture's challenges is the development of precision agriculture techniques focused on weed and crop segmentation. There are studies that show the impact of weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha. Currently, growing development of artificial vision and machine learning algorithms has allowed researchers to propose solutions for weed segmentation in different types of crops (con la finalidad de...). 
\\

One of the first approximations to the algorithms of detection of Crops was developed in 1996 \cite{brivot1996segmentation}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops. In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{cheng2015feature} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of 98\% in the identification of Weeds in the Rice, Araguez \textit{et. al} \cite{equipo2006proceedings} performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document. 
\\

Hong and Lei \cite{jeon2011robust} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%, also there had been developed an algorithm \cite{hlaing2014weed}, that through binarization methods of OTSU and Watershed for the segmentation of the images. While its classification was given through an areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed. Romeo \textit{et. al} \cite{romeo2012crop} propose to use a fuzzy clustering approach to correctly segment the crop green.
\\

The segmentation of weed and crops is not closed to color images, using a multispectral camera \cite{potena2016fast} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds. One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{di2016automatic} achieving a acceptable accuracy for the generation of Datasets. 
\\

@@

The model development for weed and maize identification algorithm using convolutional neural networks is described below.
\\
\subsection{Hardware}
\begin{comment}
Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes. Debido a la popularidad de la computacion por GPU(IDEA COMPLETADA) por sus ventajas en el desarrollo de modelos de Redes Neuronales Convolucionales, fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de clasificacion y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M. Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar el rendimiento de red en un sistema portable para su aplicacion en un sistema movil independiente . El hardware escogido sera probado para clasificar las imagenes y medir los tiempos de clasificacion para su posterior analisis. El hardware elegido será probado para clasificar imágenes, en cada clasificación se medirán los tiempos de procesamiento, para realizar un análisis si el hardware puede procesar en tiempo real 
\end{comment}

For the training and image-capturing stages, the following elements were used: a Raspberry Pi 3 with a V2.1 Pi camera for image acquisition. The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better speed processing, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA. These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M. Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in a independent mobile system that could be implemented in an embedded system. The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on analyze if the hardware can process information in real time. 
\\

@@

Also in the development stage was important the use of Linux OS , its features are: lightweight and free OS also fully compatible with the software mentioned above. For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi the Pixel OS was used for acquire images and test the classification performace of the CNN. (cambiar union de ideas)
\\

@@

Due to the lack of weed and maize plant datasets, it was necessary to search for maize crops in its initial development stage because the taken actions in this stage by the farmer will impact in the future yield of the crop (IDEA COMPLETADA). Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples. P\'illaro is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as: maize, potatoes and a wide variety of fruits. Due to its year-long production season, many maize crops at its initial development stage were found in this area. \\

@@

Samples were obtained from images captured in different maize fields. Crops were weed and maize plants could be visually discriminated were chosen in order to easy segment the images and to provide reliable samples to the network, which permit to the model to correctly learn all features of the real plant (IDEA SUSTENDAD). Maize Plants at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples. To record the samples, a camera was centered over the target plant, insuring that the capture shows all features of the maize plant. This was achieved by monitoring the obtained samples through an external display. Examples of the images captured are shown below.

@@

Also, it was necessary to obtain images of the most common weed plants found in maize crops in Pillaro, in order to allow the network to discriminate between the two defined classes in the dataset. \\
\begin{comment}
Entonces, a traves de un proceso de procesamiento digital de imagenes, como primera fase, la imagen fue normalizada en su canal verde, esto mejora la deteccion del color verde porque elimina las luces y las sombras de la imagen, despues extrajimos el color verde de la imagen con la ecuacion descrita opr Wang, Men, Luo and Mei, para obtener una imagen final en escala de grises, despues se aplico una Umbralizacion de OTSU para obtener una mascara binaria 
\end{comment}

@@

Once image processing was completed, a set of 2835 maize images and 880 weed images was obtained. Lee \textit{et. al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by means of geometric transformations. In addition, the geometric transformations \cite{sladojevic2016deep} (Si es verdad) allow overfitting reduction and improve precision in the training process. For this reason, image rotations each 30 degrees were made, obtaining an increment of the dataset by 12 times, thus increasing the chances of recognizing plants that are in any orientation effectively. \\

@@

One of the characteristics of CNN is that these can have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered: two models were chosen from the Caffe Zoo Model(it is a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}. With the four Nets chosen, each one was trained with the same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\end{table}

@@

Within parameters shown on table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was considered; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\

@@

So, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2 (QUE? corregido), then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1 (QUE corregido), followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image had a size of 16x16x16. Finally the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons. The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify, the result model is shown in the next graph.\\

@@

In training graph shown below the final result can be appreciated of the net accuracy; 9000 iterations were neccesary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy with few iterations. Note that by reducing the number of filters the network gained accuracy because the dataset does not have too many features to process, so the network obtained a better solution with a fewer number of parameters. \\

>>>>

Deep Learning has played an important role in modern times, being widely used in artificial vision applications and specifically in pattern recognition. The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture. This paper presents a study of a convolutional neural network (CNN) with two classes applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages. The algorithm has two stages, segmentation of images and classification. Segmentation is intended to separate the target plant from the original image, while classification is meant to identify what images belong to the two classes by means of a convolutional neural network previously trained with a dataset generated through the segmentation stage. The performance of the network was analyzed and compared with different network architectures. The network architecture that presented the best training results was chosen and afterwards its number of filters were reduced in order to analyze its behavior. Finally, the resulting network was tested on different processors to compare classification speed of each and determine which one could be used for an autonomous system in a real-time application.\\

\begin{comment}
-Deep Learning ha tenido un papel muy importante en los tiempos modernos, siendo muy utilizado en vision artificial y especialmente en reconocimiento de patrones, lo cual abre muchas puertas en los campos de aplicacion siendo uno de ellos la agricultura de presicion.En este paper presentamos el estudio una red neuronal convolucional aplicada a la clasificacion de plantas de maiz y de mala hierba en tiempo real, dirigida a campos de maiz en su etapa inicial.El algoritmo cuenta con dos etapas, segmentacion de imagenes y la clasificacion. En la segmentacion se busca separar de la imagen las plantas de forma individual. Mientras que la clasificacion se da a traves de la red neuronal convolucional, previamente entrenada con un dataset generado mediante la etapa de segmentacion. El rendimiento de la red se ilustra mediante analisis y comparaciones con diferentes arquitecturas de red, luego con la red que presento mejores resultados, se experimeto modificando su numero de filtros, para analizar su comportamiento. Finalmente con la red resultante se implemet\'o en diferentes procesadores para comparar tiempos de clasificacion (verdad?).
\end {comment}
\end{abstract}

@@

Technological advances have caused industry transformations; manufacturing, food processing, and information industries among others, have gone through dramatic changes with the new industrial revolution. However there are fields that have not been significantly influenced by technological development in Ecuador, as it is the case of agroindustry. Agriculture in Ecuador has undergone some changes since colonial times; while it is true that there are efficient agricultural practices, the lack of technological resources make it impossible for the country to exploit its true potential as a clean and efficient agricultural producer. Also, the excessive use of pesticides have a negative effect on the production, soil, and water quality, which leads the new research efforts towards finding alternative solutions to weed control issues. 
\\

Nowadays, one of agriculture's challenges is the development of precision agriculture techniques focused on weed and crop segmentation. There are studies that show the impact of weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha. Currently, growing development of artificial vision and machine learning algorithms has allowed researchers to propose solutions for weed segmentation in different types of crops. These algorithms are intended to be used in different weed control systems, such as autonomous weed-removing robots.
\\

One of the first approximations for crop detection algorithms was developed in 1996 \cite{brivot1996segmentation}; this algorithm could segment crops from weeds by means of infrared (IR) Images. The images were processed by a hysteresis umbral and the Min Neighbouring method to identify the rows of a crop. In recent years the implementation of machine learning has opened new possibilities in weed and crop differentiation process. Recently, the use of Harris Corner detection techniques in CNNs was implemented with the use of Feature Detection, a machine-learning algorithm that uses DBSCAN (Density-based spartial clustering of apllications with noise) \cite{cheng2015feature}. This algorithm demonstrated an effectiveness of 98\% in the identification of rice weeds. Araguez \textit{et. al} \cite{equipo2006proceedings} performed their segmentation through the  analysis of the green histogram and performing the crop and weed segmentation with unspecified classifiers in their document (revisar si esta bien 2 ultimas oraciones?). 
\\

Hong and Lei \cite{jeon2011robust} developed an approximation by using an optimal method for detection in various luminosity settings, they achived this by the use an artificial neural network (ANN) for weed and maize classification with a precision of 92.5\%. Also, another algorithm that uses OTSU and Watershed binarization methods for image segmentation has been developed \cite{hlaing2014weed}. While classification in this algorithm was done through an area analysis to perform a thresholding and the method is computationally effective when the weed distribution does not resemble the size to the crop plants, its error increases when crop density is higher compared to weeds. Romeo \textit{et. al} \cite{romeo2012crop} proposed to use a fuzzy clustering approach to correctly segment green within the crop.
\\

Weed and crop segmentation is not limited to color images. In another application  \cite{potena2016fast}, the use of a a multispectral camera  permitted to obtain RGB and NIR images for the segmentation and classification purposes. The images used a light CNN for the first process and a deep CNN for classification, its accuracy was as high as 98\% in the identification of weeds. One of the most difficult things in crop identification is the generation of datasets due to weed presence in the training images, but these can be correctly generated by the use of a CNN \cite{di2016automatic}, achieving an acceptable accuracy for the generation of datasets (verdad?). 
\\

@@

The developed model for weed and maize identification algorithm using convolutional neural networks is described below.
\\
\subsection{Hardware}
\begin{comment}
Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes. Debido a la popularidad de la computacion por GPU(IDEA COMPLETADA) por sus ventajas en el desarrollo de modelos de Redes Neuronales Convolucionales, fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de clasificacion y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M. Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar el rendimiento de red en un sistema portable para su aplicacion en un sistema movil independiente . El hardware escogido sera probado para clasificar las imagenes y medir los tiempos de clasificacion para su posterior analisis. El hardware elegido será probado para clasificar imágenes, en cada clasificación se medirán los tiempos de procesamiento, para realizar un análisis si el hardware puede procesar en tiempo real 
\end{comment}

For the training and image-capturing stages, the following elements were used: a Raspberry Pi 3 with a V2.1 Pi camera for image acquisition. The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better processing speed, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA. These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M. Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system. The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on analyze if the hardware can process information in real time. 
\\

@@

Also, the use of Linux OS in the development stages was important due to its light operating system and free OS which is also fully compatible with OpenCV.  The computer used in the project worked with Ubuntu Linux 16.04 due to its official support to CUDA, Caffe and OpenCV. Likewise, Pixel OS was used in Raspberry Pi for acquiring images and testing the CNN classification performance.
\\

@@

Due to the lack of local weed and maize plants datasets, it was necessary to search for maize crops. The initial development stage of maize was selected  because actions taken by the farmer during this stage are easier to execute and these will impact the future crop yield. Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples. P\'illaro is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as: maize, potatoes and a wide variety of fruits. Due to its year-long production season, many maize crops at its initial development stage were found in this area. \\

@@

Samples were obtained from images captured in different maize fields. Crops where weed and maize plants could be visually discriminated were chosen in order to easily segment the images and provide reliable samples to the network, which allow the model to correctly learn all features of the real plant. Maize plants at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples. To record the samples, a camera was centered over the target plant, insuring that the captured image showed all its features. This was achieved by monitoring the obtained samples through an external display. Examples of the images captured are shown below.

@@

Also, it was necessary to obtain images of the most common weed plants found in maize crops in Pillaro, in order to allow the network to discriminate between the two defined classes in the dataset: maize and weed. \\
\begin{comment}
Entonces, a traves de un proceso de procesamiento digital de imagenes, como primera fase, la imagen fue normalizada en su canal verde, esto mejora la deteccion del color verde porque elimina las luces y las sombras de la imagen, despues extrajimos el color verde de la imagen con la ecuacion descrita opr Wang, Men, Luo and Mei, para obtener una imagen final en escala de grises, despues se aplico una Umbralizacion de OTSU para obtener una mascara binaria 
\end{comment}

@@

Once image processing was completed, a set of 2835 maize images and 880 weed images was obtained. Lee \textit{et. al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by means of geometric transformations. In addition, geometric transformations \cite{sladojevic2016deep} allow overfitting reduction and improve precision in the training process. For this reason, initially obtained images were rotated every 30 degrees, obtaining an increment of the dataset by 12 times, thus increasing the chances of effectively recognizing plants that are in any orientation. \\

@@

One of the characteristics of CNN is that these can have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered. Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet. Also, Potena and Nardi used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes\cite{potena2016fast}. With the four Nets chosen, each one was trained with the same solver of type AdaDelta and with the same dataset. The training results are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\end{table}

@@

Based on the performance parameters shown on the table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was selected; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\

@@

Thus, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a value of kernel size and stride of 2. Then again a second layer of convolution that has 16 filters is applied, the size of kernel is 5 and the stride is 1, followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image had a size of 16x16x16. Finally, the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons. The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify, the result model is shown in the next graph.\\

@@

In the training graph shown below, the final net accuracy result can be appreciated; 9000 iterations were necessary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy within few iterations. Note that by reducing the number of filters the network gained accuracy because the dataset does not have too many features to process, so the network obtained a better solution with a fewer number of parameters. \\
